\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
 
\begin{document}
\title{Introduction to Particle Accelerators\\
\large Homeworks II}
\author{}
\date{}
 
\maketitle
 
\section{Synchrocyclotron}
\label{problem1}
The CERN synchrocyclotron (SC) accelerates protons up to $600$ MeV. Compute the maximum orbit radius, considering a constant magnetic field of $1.9$ T. Compute the revolution frequency as a function of the radius. Is it possible to change the radial profile of the field to obtain a constant revolution frequency as a function of the radius?

\section{Circular accelerator}
\label{problem2}
Consider a proton synchrotron with a maximum energy of $10$ GeV with a magnetic field ramping to $1.5$ T in $1$ second.

\begin{enumerate}
\item What is the proton momentum (GeV/c) when the field reaches $1.5$ T?
\item What is the value of $B\rho$ at top energy?
\item If 2/3 of the circumference are filled with bending magnets, what are $\rho$ and $R$?
\item What is the revolution frequency at $1$ GeV? At $10$ GeV?
\item What are the consequences of (4) for the rf system?
\item What is the energy gain per turn necessary to accelerate to $10$ GeV in $0.9$ s?
\item If $\phi_s$ is set to 45 degrees, what is the peak cavity voltage?
\end{enumerate}

\section{Transition energy}
\label{problem3}
$\eta$ is defined as
\begin{equation}
\frac{\Delta f}{f}= - \eta \frac{\Delta p}{p}
\end{equation}
where $\Delta$ represents the deviation with respect to the reference particle.
\begin{enumerate}
\item What is the physical meaning of $\eta$?
\item Using $\frac{\Delta R}{R} = \alpha \frac{\Delta p}{p}$; compute $\eta$ as a function of $\alpha$ and $\gamma$;
\item $\gamma_{tr}$ is the value of $\gamma$ at which $\eta =0$. What is the physical interpretation of $\gamma_{tr}$?
\item We consider three machines: the Bevatron, the CERN PS and LEAR with the values of $\alpha$ being respectively 2.42, 0.026 and -0.046. Discuss the three cases.
\end{enumerate}
\end{document}